Slight Positive Correlation Between Gendered and Racialized Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-25 outputs/paper/paper.qmd
polish charts and graphs

cleaned_search_reasons_data |>
  group_by(total_reasons, items_found) |>
  count() |>
  rename(count = n) |>
  kable(
    col.names = c("Number of Reasons", "Items_Found", "Count"),
    booktabs = TRUE
  )
```

@@

#create a scatterplot to show each observation in the dataset, comparing the number of reasons to the items found in each strip search
#colour the points based on the police division where the group of shootings occurred
#code for geom_point() referenced from https://github.com/TDonofrio62/Shooting-Occurrences-in-Toronto/blob/main/Shooting_Occurrences/outputs/paper/Shooting_Occurrences.Rmd
cleaned_search_reasons_data |>
  group_by(total_reasons, items_found, race) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = race)) +
  geom_point() +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))+
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Race"
       ) +
  scale_fill_viridis_d(option="cividis")

cleaned_search_reasons_data |>
  group_by(total_reasons, items_found, race) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = race)) +
  geom_point() +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))+
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Race"
       ) +
  scale_fill_viridis_d(option="cividis") 
```

>>>>

cleaned_search_reasons_data |>
  group_by(total_reasons, items_found) |>
  count() |>
  rename(count = n) |>
  kable(
    col.names = c("Number of Reasons", "Items Found", "Count"),
    booktabs = TRUE
  )
```

@@

#create a scatterplot to show each observation in the dataset, comparing the number of reasons to the items found in each strip search
#colour the points based on the police division where the group of shootings occurred
#code for geom_point() referenced from https://github.com/TDonofrio62/Shooting-Occurrences-in-Toronto/blob/main/Shooting_Occurrences/outputs/paper/Shooting_Occurrences.Rmd
cleaned_search_reasons_data |>
  group_by(total_reasons, items_found, race) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = race, size = count)) +
  geom_point(alpha = 0.5) +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))+
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Race"
       ) +
  scale_fill_viridis_d(option="cividis")

cleaned_search_reasons_data |>
  group_by(total_reasons, items_found, gender) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = gender, size = count)) +
  geom_point(alpha = 0.5) +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))+
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Gender"
       ) +
  scale_fill_viridis_d(option="cividis")

cleaned_search_reasons_data |>
  group_by(total_reasons, items_found, gender) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = items_found)) +
  geom_bar() +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))+
  labs(x = "Total Reasons for Strip Searching",
       y = "Items Found",
       color = "Gender"
       ) +
  scale_fill_viridis_d(option="cividis")

cleaned_race_gender_data |>
  ggplot(aes(x = income, y = count, label = ward_code)) + 
  geom_point() + 
  geom_beeswarm() +
  geom_smooth(method=lm, se=FALSE) + 
  geom_text(hjust=-0.5, vjust=0.5) + 
  labs(
    title = "Number of clinics vs. average household income for each ward",
    x = "Average household income",
    y = "Number of clinics",
    label = "Ward Code"
  ) +
  theme_minimal()
